### 2020-02-09 thesis_template/2_RelatedWork/relatedWork.tex
d
experiment plan

>>>>

Design experiment for comparing among the performance of smart pointers.

If we keep first created owner until the last phase, we can use borrowing to operate.
If we delete first created owner during the operation, we should use Rc<T>.
The question would be, we can use Rc<T> every where?

Smart pointer
    Box<T> - Box pointer lets value allocated on heap rather than on the stack.
    Rc<T> - Reference counted pointer lets variable take multiple immutable ownership.
Interier mutability
    Cell<T> - For only Copy type, it allows us to mutate variable, even if it is immutable
            Howeever, it does not support sharing the variable so that it returns always copy of the value.
    RefCell<T> - This support sharing and interier immutability for all types. This is done by allowing to get 
                mutable reference from immutable variable and push the error detacting time from compile time to runtime.

Experiment to do

Difference of operation time for 
    - T vs Box<T> vs Rc<T>
Vec<Box<T>>
&Box<T>  vs 
Vec<Rc<T>>
Vec<Rc<RefCell>>

\section{Todos}
\label{sec:history}
\begin{itemize}
    \item Document experiment of reference and dereferenced
    \item Redo the experiment with appropriate size
    \item Design experiment for reference counting(measure dropt time using criterion)
    \item Design experiment for Graph
    \item Design experiment for Multithread
    \item Study about LLVM
    \item Study about OS memory management(optional)
\end{itemize}
